Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-07-30 article_springer/article_springer.Rmd
Create pdf again
Change Title of Subsection "Weighing .. "

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output:
  html_document: default
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes

@@

# Continuous Time Random Exceedances (CTRE) {#sec:CTRE}

@@

# Scaling limit of Exceedance Times {#sec:scaling}

@@

# Mittag-Leffler Stability Plots

@@

# Fitting Mittag-Leffler Distributions {#sec:ML}

@@

**Weighing the evidence for heavy tails.**
Since the exponential distribution is nested in the Mittag-Leffler family of 
distributions, a Likelihood-ratio Test (LRT) seems to be an appropriate way to choose 
between a model with exponential and Mittag-Leffler inter-exceedance times.
Although the two models are nested, the asymptotic distribution is not 
$\chi^2_1$-distributed, and Wilk's Theorem does not hold: under $H_0$, the 
parameter $\beta$ of Mittag-Leffler distribution is equal to $1$, and hence lies
on the boundary of the parameter space $(0,1]$. 
Instead, a valid approach is a bootstrapped Likelihood-ratio test [see e.g. @davison1997bootstrap]. 
Figure \ref{Fig:LRT} displays the (simulated) power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters based on 1000 simulation runs. As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Leffler distribution from an exponential.

@@

# Inference on Exceedance times

>>>>

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output:
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes

@@

# Probabilistic Model

## Continuous Time Random Exceedances (CTRE) {#sec:CTRE}

@@

## Scaling limit of Exceedance Times {#sec:scaling}

@@

# Statistical Inference

## Mittag-Leffler Stability Plots

@@

## Fitting Mittag-Leffler Distributions {#sec:ML}

@@

## Weighing the evidence for heavy tails

Since the exponential distribution is nested in the Mittag-Leffler family of 
distributions, a Likelihood-ratio Test (LRT) seems to be an appropriate way to choose 
between a model with exponential and Mittag-Leffler inter-exceedance times.
Although the two models are nested, the asymptotic distribution is not 
$\chi^2_1$-distributed, and Wilk's Theorem does not hold: under $H_0$, the 
parameter $\beta$ of Mittag-Leffler distribution is equal to $1$, and hence lies
on the boundary of the parameter space $(0,1]$. 
Instead, a valid approach is a bootstrapped Likelihood-ratio test [see e.g. @davison1997bootstrap]. 
Figure \ref{Fig:LRT} displays the (simulated) power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters based on 1000 simulation runs. As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Leffler distribution from an exponential.

@@

## Inference on Exceedance times
